R for Clinical Study Reports and Submission

### 2021-11-06 project-folder.Rmd
Minor syntax / spelling fix

> Under the `vignettes/` folder, there are `adam/` folder and `tlf` folder.
> The `adam/` folder contains ADaM datasets.
> The `tlf` folder contains output TLFs in RTF format.
> We put `adam/` and `tlf/` folders within the `vignettes` folder only for illustration purposes.
> In an actual A&R report, you may have a different location to save your input and output.

@@

The `man/` folder is used to save documentation automatically generated by `roxygen2`.
A typical workflow is to add `roxygen2` documentation before each function in the `R/` folder.
Then `devtools::documents()` is used to generate all the documentation files in the `man/` folder.
More details can be found in [Chapter 10 of the R Packages book](https://r-pkgs.org/man.html).

@@

Reproducibility of analysis is one of the most important aspects of regulatory deliverables.
To ensure a successful reproduce, we need a controlled R environment,
including the control of the R version and the R package versions.
By using the R package folder structure and proper tools (e.g., `renv`, `packrat`),
we illustrate how to achieve reproducibility for R and R package versions.

@@

If the R version mismatch, an error message is displayed as below.

@@

- [`devtools`](https://devtools.r-lib.org/): make package development easier.
  + A good overview can be found in [Chapter 2 of the R Packages book](https://r-pkgs.org/whole-game.html).
  + `devttols::load_all()`: load all functions in `R/` folder and running environment.
  + `devtools::document()`: automatically create documentation using `roxygen2`.
  + `devttols::check()`: automatically perform compliance check as an R package.
  + `devtools::build_site()`: automatically run analysis scripts in batch and create a `pkgdown` website.
- [`usethis`](https://usethis.r-lib.org/): automates repetitive tasks that arise during project setup and development.
- [`testthat`](https://testthat.r-lib.org/): streamline testing code.
  + A discussion of using the `testthat` for an A&R project can be found in (@madhutest).
- [`pkgdown`](https://pkgdown.r-lib.org/): generate static HTML documentation website for an R package
  + It also allows you to run all analysis code in batch.

>>>>

> Under the `vignettes` folder, there are two folders: `adam` folder and `tlf` folder.
> The `adam` folder contains ADaM datasets.
> The `tlf` folder contains output TLFs in RTF format.
> We put `adam` and `tlf` folders within the `vignettes` folder only for illustration purposes.
> In an actual A&R report, you may have a different location to save your input and output.

@@

The `man/` folder is used to save documentation automatically generated by `roxygen2`.
A typical workflow is to add `roxygen2` documentation before each function in the `R/` folder.
Then `devtools::document()` is used to generate all the documentation files in the `man/` folder.
More details can be found in [Chapter 10 of the R Packages book](https://r-pkgs.org/man.html).

@@

Reproducibility of analysis is one of the most important aspects of regulatory deliverables.
To ensure a successful reproduction, we need a controlled R environment,
including the control of the R version and the R package versions.
By using the R package folder structure and proper tools (e.g., `renv`, `packrat`),
we illustrate how to achieve reproducibility for R and R package versions.

@@

If there is a R version mismatch, an error message is displayed as below.

@@

- [`devtools`](https://devtools.r-lib.org/): make package development easier.
  + A good overview can be found in [Chapter 2 of the R Packages book](https://r-pkgs.org/whole-game.html).
  + `devtools::load_all()`: load all functions in `R/` folder and running environment.
  + `devtools::document()`: automatically create documentation using `roxygen2`.
  + `devtools::check()`: automatically perform compliance check as an R package.
  + `devtools::build_site()`: automatically run analysis scripts in batch and create a `pkgdown` website.
- [`usethis`](https://usethis.r-lib.org/): automates repetitive tasks that arise during project setup and development.
- [`testthat`](https://testthat.r-lib.org/): streamline testing code.
  + A discussion of using the `testthat` for an A&R project can be found in (@madhutest).
- [`pkgdown`](https://pkgdown.r-lib.org/): generate static HTML documentation website for an R package
  + It also allows you to run all analysis code in batch.
